---
title: "Trends in IO Psychology"
output: rmarkdown::github_document
---


## Trends in Industrial and Organizational Psychology
As scientists search for new insights into the world of work, topics inevitably fall in and out of vogue. Perhaps the most volatile and well recognized swings in research interests have been observed in personality research. Walter Mischel's 1968 book *Personality and Assessment* came to the gloomy conclusion that "With the possible exception of intelligence, highly generalized behavioral consistencies have not been demonstrated, and the concept of personality traits as broad response predispositions is thus untenable". After this book was published, personality research for selection and assessment slowed considerably until about a decade later. Identifying these trends (and slumps) can help researchers and practitioners see where the field is headed, where it has been, and identify ideas and topics that should be brought to light once again. 

This app was designed to help researchers and practitioners identify current trends in industrial and organizational psychology. It uses user defined queries to search article abstracts in the IO psychology's top scientific journals. Users are provided with a plot of trends over time with options to focus on specific journals, a downloadable .csv file, and a regression results using the user's search term to predict citation rate across the decades. Feel free to download and adapt the app how you see fit or submit a request and I will see if I can help. 

To run the app without downloading the repository, simply run the following code.

```{r, eval=FALSE}
shiny::runGitHub("trends_in_IO", username = "jimmyrigby94")
```

Alternatively, you can download the repository and run the following code.

```{r, eval=FALSE}
# First clone the repository with git. If you have cloned it into
# ~/shiny_example, first go to that directory, then use runApp().
setwd("~/shiny_example")
runApp()
```

